\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation

### 2024-03-11 Articles/IROS/root.tex
comments
added field visualization

@@

\comment{}{we dont have the close obstacles bottlenecks}

>>>>

\alert{remove the above equation and add a vector of calculated velocities equation instead}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\linewidth]{demo-field1.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:example-field}
\end{figure}

\comment{}{we dont have the close obstacles bottlenecks, we do have weird bottlenecks in the orthagonal directions - maybe}
